SAT Competition 2020\tnoteref{title}

### 2021-06-22 paper/main.tex

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings. \textcolor{red}{Add various references to the several things in this sentence}

@@

Complementing the generality advocated by the standard SAT Competition tracks, in which solvers are evaluated
on a set of benchmarks including instances from various types of different problem domains, for 2020 
the organizers aimed to experiment with the potential of a more application-specific track,
each year highlighting a different problem domain where the SAT solving technology helps to advance the state of the art.
In 2020, the Planning track represented the first trial instantiation of this idea.
The focus of this track was specifically on efficiently solving
instances arising from the domain of SAT-based automated planning.\textcolor{red}{Add references} 
Automated planning was chosen as the target problem domain of this first instantiation of the domain-specific tracks
due to its centrality as one of the first breakthrough applications of SAT solvers.
To this end, solvers participating in the Planning
track were evaluated on 200 benchmark instances encoding planning problems.
The same rules for participation as in the Main track applied to the Planning track.
Solvers submitted to the Main track automatically participated in the Planning track.

The traditional Hack track (established 
2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}\textcolor{red}{Add reference}. 
In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
Hack tracks encourage participation of such small modifications. 
The limit for being considered a ``hack'' was---somewhat arbitrarily\footnote{The specific threshold for edit distance is not central here; the idea is essentially to only allow relatively small changes to the Glucose
code base, i.e., ``quick hacks'' to Glucose.}---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
Unfortunately, in 2020 there were not enough participants in this sub-track and so we do not report on it in the results section.

@@

The Incremental Library track was first introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
In the Incremental Library track the underlying idea is to mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.\textcolor{red}{Should we not cite the 2004 temporal induction paper by Niklases here?}
Examples for applications of incremental SAT solving are counterexample-guided abstraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

@@

The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.
The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on AWS\textcolor{red}{Was AWS spelled out a single time before this? I now notice that
we do not really mention Amazon much, should we mention it more specifically?}
 m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

\textcolor{red}{Hmm we don't have any result tables or anything??}

@@

A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
With these
 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
We can see that the further iterations tend to add very little,
with the final four iterations adding one instance each. Note that each solver
that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
shows up in the greedy set cover.
% for example the case of the last listed  
%\solver{exp-V-LGB-MLD-CBT-DL}.
Highlighting solvers that uniquely solve instance is a property of the greedy set cover metric
which we believe is congruent with documenting contributions to the state of the art.
\textcolor{red}{congruent...? maybe a better choice of words here?}

>>>>

From what was once mainly the archetypal intractable (in particular NP-complete) problem, propositional satisfiability 
(or Boolean satisfiability, SAT) has flourished into a success story of modern computer science~\cite{DBLP:series/faia/2009-185}.
This is due to advances in SAT solvers, i.e., implementations of decision procedures for SAT, which today form a 
central computational tool for solving real-world problem instances of various kinds of NP-hard search and optimization problems.
With standardized input formats, readily-available APIs for incremental applications,
and certified proof logging and checking capabilities, applications of SAT solver technology
have branched from the first breakthrough applications in automated planning, test pattern generation and hardware verification
to thousands of different application settings.

@@

Complementing the generality advocated by the standard SAT Competition tracks, in which solvers are evaluated
on a set of benchmarks including instances from various types of different problem domains, for 2020 
the organizers aimed to experiment with the potential of a more application-specific track,
each year highlighting a different problem domain where the SAT solving technology helps to advance the state of the art.
In 2020, the Planning track represented the first trial instantiation of this idea.
The focus of this track was specifically on efficiently solving
instances arising from the domain of SAT-based automated planning~\cite{Kautz1992}.
Automated planning was chosen as the target problem domain of this first instantiation of the domain-specific tracks
due to its centrality as one of the first breakthrough applications of SAT solvers.
To this end, solvers participating in the Planning
track were evaluated on 200 benchmark instances encoding planning problems.
The same rules for participation as in the Main track applied to the Planning track.
Solvers submitted to the Main track automatically participated in the Planning track.

The traditional Hack track (established 
2009 as \solver{Minisat} Hack track) was organized as a sub-track of the Main track for hacks of \solver{Glucose 3}~\cite{Audemard:2018:Glucose}.
In the past, several advances in SAT solving required only small modifications of an established solver to achieve a considerable contribution. 
Hack tracks encourage participation of such small modifications. 
The limit for being considered a ``hack'' was---somewhat arbitrarily\footnote{The specific threshold for edit distance is not central here; the idea is essentially to only allow relatively small changes to the Glucose
code base, i.e., ``quick hacks'' to Glucose.}---set to 1000 non-space character edit distance from the sources of \solver{Glucose 3}. 
Unfortunately, in 2020 there were not enough participants in this sub-track and so we do not report on it in the results section.

@@

The Incremental Library track was first introduced in SAT~Race~2015~\cite{Balyo:2015:SATRace} and also took place in SAT~Competitions 2016 and 2017.
In the Incremental Library track the underlying idea is to mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Niklas:2003:Incremental,Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.
Examples for applications of incremental SAT solving are counterexample-guided abstraction refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based planning~\cite{Balyo:2017:IncrPlanning},
multi-agent path finding~\cite{DBLP:conf/ijcai/Surynek19}, and satisfiability modulo theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.

@@

The Incremental Library Track was run on computers with 2x Intel Xeon E5430 \SI{2.66}{\giga\hertz}
(4-Core) processors and \SI{24}{\giga\byte} of RAM.
The Parallel track was run on AWS m4.16xlarge machines with 64 virtual CPUs and 256 GB
of memory, while the Cloud track was run on Amazon Web Services (AWS)
 m4.4xlarge machines with 16 virtual CPUs and 64 GB of
memory. These tracks used wall-clock timeouts of \SI{5000}{\second} and \SI{1000}{\second}, respectively.

@@

@@

A greedy set cover of the solved instances by solvers of the Main track is presented in Table~\ref{tab:gscMain}. 
In the first iteration, the solver which solved the highest number of instances is selected; in our case it was \solver{Kissat-sat} with 264 instances as we know already from Table~\ref{tab:results}.
With these
 264 instances already covered, \solver{CaDiCaL-alluip} is the best in further contributing to the set by additional $22$ instances in iteration $2$.
We can see that the further iterations tend to add very little,
with the final four iterations adding one instance each. Note that each solver
that managed to solve an instance uniquely (i.e., being the only solver that solved a particular instance)
shows up in the greedy set cover.
% for example the case of the last listed  
%\solver{exp-V-LGB-MLD-CBT-DL}.
Highlighting solvers that uniquely solve instance is a property of 
Indeed, the greedy set cover metric highlights solvers which are able to uniquely solve specific benchmark instances
and thereby contributing to the current state of the art.
